Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Word Processors

### 2018-08-01 main.tex
Reset Howard's changes in the abstract-approach after discussions with Moritz.

\noindent\textbf{Approach:} Bruce Miller at the \gls*{nist} developed a collection of semantic \LaTeX{} macros that create links from mathematical symbols to their definitions in the \gls*{nist} \gls*{dlmf}. We are using these macros to perform rule-based translations between the formulae in the \gls*{dlmf} and \gls*{cas}. Moreover, we develop software to ease the creation of new rules and to discover inconsistencies.

>>>>

\noindent\textbf{Approach:} The \gls*{nist} developed a collection of special \LaTeX{} macros that create links from mathematical symbols to their definitions in the \gls*{nist} \gls*{dlmf}. We are using these macros to perform rule-based translations between the formulae in the \gls*{dlmf} and \gls*{cas}. Moreover, we develop software to ease the creation of new rules and to discover inconsistencies.
